\textit{Supporting Information for}: Memory for television episodes preserves event content while introducing new across-event similarities

### 2020-02-18 paper/supporting_information.tex

Two other parameters ultimately affect this balance between preserving local and global structure: the seed ($\tau$) for the (pseudo-)random number generator, and the order of the observations (i.e., trajectories) to be embedded ($\phi$).  As described in \textit{Methods}, we ensured the video and recall events were projected onto the \textit{same} low-dimensional manifold by fitting the embedding model to a stacked matrix of all video, average recall, and individuals' recall events.  After initializing the low-dimensional simplicial set (by default, using a spectral embedding of the high-dimensional simplicial set's fuzzy 1-skeleton), UMAP optimizes the embedding using stochastic gradient descent with cross-entropy as a cost function.  During optimization, indices of the data are sampled at random, and thus the local minimum achieved by the optimization is dependent on both the state of the RNG and the sequence in which observations are concatenated.

>>>>

Two other parameters ultimately affect this balance between preserving local and global structure: the seed ($\tau$) for the (pseudo-)random number generator, and the order of the observations (i.e., trajectories) to be embedded ($\varphi$).  As described in \textit{Methods}, we ensured the video and recall events were projected onto the \textit{same} low-dimensional manifold by fitting the embedding model to a stacked matrix of all video, average recall, and individuals' recall events.  After initializing the low-dimensional simplicial set (by default, using a spectral embedding of the high-dimensional simplicial set's fuzzy 1-skeleton), UMAP optimizes the embedding using stochastic gradient descent with cross-entropy as a cost function.  During optimization, indices of the data are sampled at random, and thus the local minimum achieved by the optimization is dependent on both the state of the RNG and the sequence in which observations are concatenated.
